\TITLE

### 2021-01-27 final/vonLaszewski-covid.tex
80 char formatting

    \begin{subfigure}{.49\textwidth}
      \centering
      \includegraphics[width=1.0\linewidth]{images/predict/Fig4a.pdf}  
      \caption{Prediction accuracy for deaths.}
      \label{fig:magic-a}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
      \centering
      \includegraphics[width=1.0\linewidth]{images/predict/Fig4b.pdf}        
      \caption{Prediction accuracy for cases.}
      \label{fig:magic-b}
    \end{subfigure}

@@

\begin{figure}[!p]
    \centering
    \includegraphics[width=1.0\textwidth]{images/boxwhisker/boxplot_casesNEW2.pdf}
    \vspace{-1cm}
    \caption{Influence of risk factors on the accuracy of the
      prediction of COVID-19 cases. The y-axis represents the
      cumulative error over all input data for the cities. The x-axis labels correspond to the order of models for minimum model error.}
    \label{fig:box-cases}
    \bigskip

    \includegraphics[width=1.0\textwidth]{images/boxwhisker/boxplot_deathNEW2.pdf}
    \vspace{-1cm}
    \caption{Influence of risk factors on the accuracy of the
      prediction of COVID-19 deaths. The y-axis represents the
      cumulative error over all input data for the cities. The x-axis labels correspond to the order of models for minimum model error.}
    \label{fig:box-death}
\end{figure}

@@

\begin{figure}[!h]
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/predict/Length_5-fields_pop_density_2010-Cumulative-Cases.pdf}
    %\vspace{-1cm}
    \caption{Model prediction error cases.}
    \label{fig:error-case-popdensity}
  \end{subfigure}
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/predict/Length_5-fields_pop_density_2010-Cumulative-Death.pdf}
    %\vspace{-1cm}
    \caption{Model prediction error deaths.}
    \label{fig:error-death-popdensity}
    \end{subfigure}

@@

% In case of cases we also see a drop in the better
% model predictions.

\begin{figure}[!htbp]
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_DeathNEW3.pdf}
        \caption{Cumulative error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_CasesNEW3.pdf}
        \caption{Cumulative error for cases.}
        \label{fig:place-top10-cases}
    \end{subfigure}

@@

\begin{enumerate}
    \item The entire cloudmesh code on which the cloud based implementation of the AICov framework is based and contains over 70 contributors is available publicly at \url{https://github.com/cloudmesh}. Cloudmesh contains a number of modules that dependent on the users access to cloud resources can be customized. A detailed manual about the configuration is available at \url{https://cloudmesh.github.io/cloudmesh-manual/}.

@@

    However, as a publication is pending, at this time, the use of the data is copyrighted and can not be used for other publications without contacting the authors. The data gathering and analysis is a significant intellectual contribution and we like to avoid that the data is taken before we have not secured a publication.

@@

%\clearpage
%\singlespace
%\maketitle
%\input{response-v3-content}

\clearpage
\input{response-v4-content}

>>>>

    \begin{subfigure}{.49\textwidth}
      \centering
      \includegraphics[width=1.0\linewidth]{images/Fig4a.pdf}  
      \caption{Prediction accuracy for deaths.}
      \label{fig:magic-a}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
      \centering
      \includegraphics[width=1.0\linewidth]{images/Fig4b.pdf}        
      \caption{Prediction accuracy for cases.}
      \label{fig:magic-b}
    \end{subfigure}

@@

\begin{figure}[!p]
    \centering
    \includegraphics[width=1.0\textwidth]{images/boxplot_casesNEW2.pdf}
    \vspace{-1cm}
    \caption{Influence of risk factors on the accuracy of the
      prediction of COVID-19 cases. The y-axis represents the
      cumulative error over all input data for the cities. The x-axis labels correspond to the order of models for minimum model error.}
    \label{fig:box-cases}
    \bigskip

    \includegraphics[width=1.0\textwidth]{images/boxplot_deathNEW2.pdf}
    \vspace{-1cm}
    \caption{Influence of risk factors on the accuracy of the
      prediction of COVID-19 deaths. The y-axis represents the
      cumulative error over all input data for the cities. The x-axis labels correspond to the order of models for minimum model error.}
    \label{fig:box-death}
\end{figure}

@@

\begin{figure}[!h]
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/Length_5-fields_pop_density_2010-Cumulative-Cases.pdf}
    %\vspace{-1cm}
    \caption{Model prediction error cases.}
    \label{fig:error-case-popdensity}
  \end{subfigure}
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/Length_5-fields_pop_density_2010-Cumulative-Death.pdf}
    %\vspace{-1cm}
    \caption{Model prediction error deaths.}
    \label{fig:error-death-popdensity}
    \end{subfigure}

@@

\begin{figure}[!htbp]
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/PlaceTop10_DeathNEW3.pdf}
        \caption{Cumulative error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/PlaceTop10_CasesNEW3.pdf}
        \caption{Cumulative error for cases.}
        \label{fig:place-top10-cases}
    \end{subfigure}

@@

\begin{enumerate}

\item The entire cloudmesh code on which the cloud based
  implementation of the AICov framework is based and contains over 70
  contributors is available publicly at
  \url{https://github.com/cloudmesh}. Cloudmesh contains a number of
  modules that dependent on the users access to cloud resources can be
  customized. A detailed manual about the configuration is available
  at \url{https://cloudmesh.github.io/cloudmesh-manual/}.

@@

  However, the use of the data is copyrighted and must be authorized
  to be used for other publications without contacting the
  authors. The data gathering and analysis is a significant
  intellectual contribution and we like to avoid that the data is
  taken before we have not secured a publication.

@@
